---
title: "OpenIntro Lab - Probability"
author: "HulkMeyer"
date: "`r Sys.Date()`"
output: pdf_document
---

# OpenIntro Lab - Probability
## The Hot Hand
### Loading libraries
```{r message=FALSE, warning=FALSE, include=FALSE, paged.print=FALSE}
library(tidyverse)
library(openintro)
```

### Dataset
Will be working with the Kobe Bryant basketball set from the 2009 NBA Finals
```{r}
glimpse(kobe_basket)
```
### Exercise 1
What does a streak length of 1 mean, i.e. how many hits and misses are in a streak of 1? What about a streak length of 0?
**Calculating Kobe Streaks
```{r}
kobe_streak <- calc_streak(kobe_basket$shot)
ggplot(data = kobe_streak, aes(x = length)) +
  geom_bar()
```
The number given to the length of streak represents the number of consecutive shots that Kobe made in a row.  so a streak of 0 is if Kobe broke a streak and had not made a shot yet a streak of 1 would be a made shot followed by a miss.  2 is making 2 shots and then missing.  It appears that his longest streak is 4 made shots without a miss. 

### Exercise 2
Describe the distribution of Kobe’s streak lengths from the 2009 NBA finals. What was his typical streak length? How long was his longest streak of baskets? Make sure to include the accompanying plot in your answer.
```{r}
ggplot(data = kobe_streak, aes(x = length)) +
  geom_bar()
```
In the 2009 NBA Finals Kobe's typical streak was given he had made 1 shot was a 1 shot streak (24 occurances), his longest streak was 4 made shots (1 occurance)
## Setting the stage Simulations in R
### Flipping a coin
```{r}
coin_outcomes <- c("heads", "tails")
set.seed(0) 
sim_fair_coin <- sample(coin_outcomes, size = 100, replace = TRUE)
sim_fair_coin
```
```{r}
table(sim_fair_coin)
```

### Exercise 3 - Simulations (Coin Flips)
In your simulation of flipping the unfair coin 100 times, how many flips came up heads? Include the code for sampling the unfair coin in your response. Since the markdown file will run the code, and generate a new sample each time you Knit it, you should also “set a seed” before you sample. Read more about setting a seed below.
```{r}
set.seed(0) 
sim_unfair_coin <- sample(coin_outcomes, size = 100, replace = TRUE, 
                          prob = c(0.2, 0.8))
sim_unfair_coin
```
```{r}
table(sim_unfair_coin)
```

###Exercise 4 - Independent Shooter
What change needs to be made to the sample function so that it reflects a shooting percentage of 45%? Make this adjustment, then run a simulation to sample 133 shots. Assign the output of this simulation to a new object called sim_basket.
```{r}
set.seed(0) 
shot_outcomes <- c("H", "M")
sim_basket <- sample(shot_outcomes, size = 133, replace = TRUE, 
                          prob = c(0.45, 0.55))
sim_basket
```
Summantions
```{r}
table(sim_basket)
```
#Exercise 5
Using calc_streak, compute the streak lengths of sim_basket, and save the results in a data frame called sim_streak.
```{r}
kobe_streak <- calc_streak(kobe_basket$shot)
ind_shooter_streak <- calc_streak(sim_basket)
```

# Exercise 6
Describe the distribution of streak lengths. What is the typical streak length for this simulated independent shooter with a 45% shooting percentage? How long is the player’s longest streak of baskets in 133 shots? Make sure to include a plot in your answer.
```{r}
ggplot(data = ind_shooter_streak, aes(x = length)) +
  geom_bar()
```
The independent shooter has streak level 1 (20 occurances) and longest streak of 4 (4 occurances)

# Exercise 7
If you were to run the simulation of the independent shooter a second time, how would you expect its streak distribution to compare to the distribution from the question above? Exactly the same? Somewhat similar? Totally different? Explain your reasoning.

I would expect the distribution to generally product the same number of made shots, but the streak length would not be the same over the same 133 shot attempts.  I would expect the most variation to come in the distribution of shot streaks vs. overall made shots. 

# Exercise 8
How does Kobe Bryant’s distribution of streak lengths compare to the distribution of streak lengths for the simulated shooter? Using this comparison, do you have evidence that the hot hand model fits Kobe’s shooting patterns? Explain.
```{r}
table(kobe_basket$shot)
```


When comparing the 2 distributions, we can see that Kobe has more 1 and 3 shot streaks than the independent shooter but less 2 and 4 shot streaks than the independent shooter.  
Overall Kobe hit 58 shots and the Ind_shooter hit 60 shots both over 133 shots.  
I do not believe that this data allows you to say that Kobe had a hot hand in the 2009 NBA Finals






















